---
title: "PQHS471_AndrewShan_Hw4"
author: "Andrew Shan"
date: "2/26/2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r}
library(MASS)
attach(Boston)
```
```{r}
dim(Boston)
names(Boston)
```

# Estimate $\hat{\mu}$
```{r}
mu.hat <- mean(medv)
mu.hat
```

# Estimate of the standard error of $\hat{\mu}$

```{r}
se.hat<- sd(medv)/ sqrt(dim(Boston)[1])
se.hat
```


# Bootstrap estimate of standard error 
```{r}
library(boot)
set.seed(471)
boot.fn<-function(data,index){
  mu <- mean(data[index])
  return(mu)
}
boot(Boston$medv, boot.fn, 10000)
```

The bootstrap returns the standard error of $\hat{\mu}$, 0.4046, which is very close to 0.4089.

# 95% confidence interval

```{r}
t.test(Boston$medv)
```
```{r}
CI <- c(22.53281- 2*0.4046056, 22.53281+ 2*0.4046056)
CI
```

Boostrap 95% confidence interval is very close to t.test confidence interval.

# Estimate median of $\hat{\mu}$

```{r}
med.hat <- median(Boston$medv)
med.hat
```

# Estimate standard error of $\hat{\mu}$

```{r}
set.seed(471)
median.fn<-function(data,index){
  mu <- median(data[index])
  return(mu)
}
boot(Boston$medv, median.fn, 10000)
```

The bootstrap returns a same median 21.2 but a smaller standard error compared to mean standard error. 

# Tenth percentile of medv

```{r}
quantity <- quantile(Boston$medv, 0.1)
quantity
```


# bootstrap to estimate the standard error
```{r}
set.seed(471)
quantity.fn<-function(data,index){
  mu <- quantile(data[index],0.1)
  return(mu)
}
boot(Boston$medv, quantity.fn, 10000)
```

The boostrap returns same result of 10th percentile and a small standard error of 0.5026.